---
title: "Auguste_9041_Lab_2"
author: "Ronald Auguste"
date: today
format: 
    html:
      toc: true
      code-fold: true
      code-summary: "Show code"
      df-print: paged
execute:
    echo: false
    warning: false
---

```{r, initial setup}
#| output: FALSE
#loading libraries and data
library(tidyverse)
library(psych)
library(readxl)
library(gt)
library(janitor)

Attachment_Anxiety_Data <- read_excel("./Attachment_Anxiety_Data.xlsx")
```

```{r, cleaning and mutating data}
#| output: FALSE
#cleaning and mutating data
Attachment_Anxiety_Data_clean <- Attachment_Anxiety_Data |> 
  mutate(
    Gender = factor(Gender,
                    levels = c(1,2),
                    labels = c("male", "female")),
    `Age group` = factor(`Age group`,
                         levels = c(1:5),
                         labels = c("18-24", "24-34", "35-44", "45-54", "55-64")),
    Relationship = factor(Relationship,
                          levels = c(1, 2, 4, 5, 6, 7),
                          labels = c("married", "in a relationship", "divorced", "in a relationship", "never been in a relationship", "prefer not to                           say" )),
    Ethnicity = factor(Ethnicity,
                       levels = c(1, 2, 5, 6),
                       labels = c("white/Caucasian", "Asian/Asian British", "Other ethnic group", "prefer not to say"))
  ) |> 
  mutate(across(c(SA_1:SA_20, AA_1:AA_9, SEst_1:SEst_10), as.integer)) 
#cleaning process: added informative labels to demographics and converted to 
#factor (extra step but probably useful for later analyses); converted all 
#surveys columns to integer (separated each survey for clarity)
```

```{r, creating answer keys}
#| output: FALSE
#creating answer keys using list()
SA_keys <- list(Social_Interaction_Anxiety = c("SA_1","SA_2","SA_3","SA_4",
                                               "-SA_5","SA_6","SA_7","SA_8",
                                               "-SA_9","SA_10","-SA_11",
                                               "SA_12","SA_13","SA_14",
                                               "SA_15","SA_16","SA_17",
                                               "SA_18","SA_19","SA_20")
)
AA_keys <- list(Attachment_Anxiety = c("AA_1","AA_2","AA_3","AA_4","AA_5",
                                       "AA_6","AA_7","AA_8","AA_9")
)
SEst_keys <- list(Self_Esteem = c("SEst_1","-SEst_2","SEst_3","SEst_4",
                                  "-SEst_5","-SEst_6","SEst_7","-SEst_8",
                                  "-SEst_9","SEst_10")
)
```

```{r, computing alphas etc}
#| output: FALSE
#computing Cronbach's alpha etc for each scale
SA_scores <- scoreItems(SA_keys, Attachment_Anxiety_Data_clean, totals = F, min = 1, max = 5)

AA_scores <- scoreItems(AA_keys, Attachment_Anxiety_Data_clean, totals = F, min = 1, max = 7)

SEst_scores <- scoreItems(SEst_keys, Attachment_Anxiety_Data_clean, totals = F, min = 1, max = 4)

#converting lists to dataframes
SA_scores.df <- as.data.frame(SA_scores$scores)
AA_scores.df <- as.data.frame(AA_scores$scores)
SEst_scores.df <- as.data.frame(SEst_scores$scores)

#combining dataframes
Allscores.df <- cbind(SA_scores.df, AA_scores.df, SEst_scores.df)

Attachment_Anxiety_wAverages <- cbind(Attachment_Anxiety_Data_clean, Allscores.df)

#reducing dataframe
Attachment_Anxiety_Reduced <- select(Attachment_Anxiety_wAverages, URN, Gender, 
                                     `Age group`, Relationship, Ethnicity, 
                                     Social_Interaction_Anxiety, 
                                     Attachment_Anxiety, Self_Esteem) |> 
  mutate_if(is.numeric, round, 2)
```

```{r, demographic tables}
#|output: FALSE
#creating demographic table
demographic_table <- Attachment_Anxiety_Reduced |> 
  tabyl(Gender, `Age group`)

gttable.1 <- demographic_table |>
  gt() |>
  tab_header(
    title = md("*Distribution of Males and Females by Age Group*")
  )
```

```{r, score tables}
#| output: FALSE 
#creating score table
summary <-  Attachment_Anxiety_Reduced |> 
 select(Social_Interaction_Anxiety, Attachment_Anxiety, Self_Esteem) |> 
  describe()
summary
```

```{r, extracting sample size}
#| output: FALSE
#extracting sample size
n <- (summary)[1,2]
# n <- (describe(Attachment_Anxiety_Reduced))[1,2]
```

```{r, Scales column}
#| output: FALSE
#creating a "Scales" column and adding it to summary
Scales <- c("Social Interaction Anxiety", "Attachment Anxiety", "Self Esteem")
summary$Scales <- Scales
#n.b. code works, but viewing "summary" after adding "Scales" throws this error:
#Error in Math.data.frame(list(vars = 1:3, n = c(63, 63, 63), mean = c(2.68888888888889,  : 
#non-numeric-alike variable(s) in data frame: Scales
#This is why (from Claude.ai):
#Your code is fine. The problem is in viewing or printing the result.
#summary$Scales <- Scales works: the new column is added without any error. The 
#trouble is that describe() returns an object with the class "psych/describe" on 
#top of data.frame, and when you print or view it, psych's print method calls 
#round() on the whole object. round() goes through Math.data.frame, which refuses 
#to run if any column is non-numeric. Your character column Scales triggers that, 
#and that's the error you saw.
```

```{r, score table}
#| output: FALSE
#creating a score table
alphas <- round(c(
  SA_scores$alpha,
  AA_scores$alpha,
  SEst_scores$alpha
), 2)

#selecting variables from summary table
summary_reduced <- summary |> 
  select(Scales, mean, median, sd, range) |> 
  mutate_if(is.numeric, round, 2)

#reduced summary table with alphas
summaries_w_alphas <- cbind(summary_reduced, alphas)
```

```{r, reproducible table}
#| output: FALSE
#creating reproducible table with gt()
gttable.2 <- gt(summaries_w_alphas) |>
  tab_header(
    title = md("*Descriptive Statistics for Attachment and Social Anxiety Scales*")) |>
  tab_stubhead(label= "Composites")|>
  tab_spanner(
    label="Central Tendency",
    columns = c(mean, median)
  )|>
  tab_spanner(
    label="Variability",
    columns = c(sd, range)
  )|>
  tab_spanner(
    label="Reliability Values (Chronbach's alpha)",
    columns = c(alphas)
  ) 
```

```{r, Asian/Asian British participants}
#| output: FALSE
#filtering for Asian/Asian British only
Attachment_Anxiety_Reduced_Asian <- Attachment_Anxiety_Reduced |> 
  filter(Ethnicity == "Asian/Asian British")
#n.b. filter only worked for label "Asian/Asian British", not level "2"

#filtered score table
#creating score table
summary_Asian <-  Attachment_Anxiety_Reduced_Asian |> 
  select(Social_Interaction_Anxiety, Attachment_Anxiety, Self_Esteem) |> 
  describe()
summary_Asian

#extracting sample size
n_Asian <- (summary_Asian)[1,2]
# n_Asian <- (describe(Attachment_Anxiety_Reduced_Asian))[1,2]

#using previous "Scales" column and adding it to summary_Asian

summary_Asian$Scales <- Scales
#n.b. see previous note about "error"

#creating a score table
#alphas created during equivalent step with unfiltered data

#selecting variables from summary table
summary_Asian_reduced <- summary_Asian |> 
  select(Scales, mean, median, sd, range) |> 
  mutate_if(is.numeric, round, 2)

#reduced summary table with alphas
summaries_Asian_w_alphas <- cbind(summary_Asian_reduced, alphas)

#creating reproducible table with gt()
gttable.2.Asian <- gt(summaries_Asian_w_alphas) |>
  tab_header(
    title = md("*Descriptive Statistics for Attachment and Social Anxiety Scales*")) |>
  tab_stubhead(label= "Composites")|>
  tab_spanner(
    label="Central Tendency",
    columns = c(mean, median)
  )|>
  tab_spanner(
    label="Variability",
    columns = c(sd, range)
  )|>
  tab_spanner(
    label="Reliability Values (Chronbach's alpha)",
    columns = c(alphas)
  ) |> 
  tab_footnote(
    footnote = md("*Descriptives for Asian/British Asian participants*"),
    locations = cells_title(groups = "title")
    ) |> 
      tab_style(
        style = cell_text(align = "right"),
        locations = cells_footnotes()
  )|>
  tab_options(
    table.border.bottom.style = "none"
  )
```

## Intro

## Methods

### Participants
In this data set there were `{r} n` participants, across five age-groups (Table 1).

`{r} gttable.1`

### Measures
In this Attachment and Social Anxiety data set, the 3 scales refer to participants' average scores on measures of social anxiety, attachment anxiety and self-esteem. The Social Interaction Anxiety scale is a 20-item survey that measures distress and fear experienced in social interactions (Cronbach's alpha = `{r} alphas[1]`). The shortened Attachment-Related Anxiety scale is a 9-item subscale of the Experiences in Close relationships Scale (Cronbach's alpha = `{r} alphas[2]`); it measures a person’s level of fear, insecurity, and hypervigilance regarding rejection, abandonment, and emotional distance in close relationships. The Rosenberg Self-Esteem Scale is a 10-item survey that measures global self-esteem and overall feelings of self-worth or self-acceptance (Cronbach's alpha = `{r} alphas[3]`).

### Data Analysis Strategy
The data for items SA_5, SA_9, and SA_11 on the social anxiety scale, and items SEst_2, SEst_5, SEst_6, SEst_8, and SEst_9 on the self-esteem scale scale were reverse coded. 

## Results
`{r} gttable.2`
In this Attachment and Social Anxiety data set, the 3 scales refer to participants' average scores on measures of social anxiety, attachment anxiety and self-esteem. Participants had a mean score on social anxiety of `{r} summaries_w_alphas[1,2]`, on attachment anxiety of `{r} summaries_w_alphas[2,2]`, and on self esteem of `{r} summaries_w_alphas[3,2]`. 

`{r} gttable.2.Asian`
When only including participants of Asian/Asian British ethnicity, the 3 scales refer to social anxiety, attachment anxiety and self-esteem statistics for that particular subgroup. Participants had a mean score on social anxiety of `{r} summaries_Asian_w_alphas[1,2]`, on attachment anxiety of `{r} summaries_Asian_w_alphas[2,2]`, and on self-esteem of `{r} summaries_Asian_w_alphas[3,2]`.

## Discussion
Asian/Asian British descriptives pretty similar to those of the full sample. 